Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-04-26 manuscript.Rmd
Updated csv files. Mistake.

```{r plotSmallMultiples}
hIndex.df <- arrange(hIndex, desc(h5Median)) %>% select(title, h5Median)
hIndex.df$top10 <- NA
hIndex.df$top10[1:10] <- "yes"
hIndex.df$top10[11:nrow(hIndex.df)] <- "no"
hIndex.df <- data.frame(hIndex.df)

@@

sm.df$top10 <- ifelse(is.na(sm.df$top10), "no", sm.df$top10)

@@

x.df <- data.frame(title = Overall.N$title, label = title$Overall.N)

xpos = rep(10, 78)
ypos = rep(130, 78)
lab <- Overall.N$Overall.N
title2 <- unique(sm.df$title2)

@@

ggplot(sm.df, aes(year, N, group = 1)) + geom_line(aes(colour = top10)) + 
facet_wrap( ~ title2, ncol=7) +
theme_bw() +
theme(panel.grid.major = element_blank(), 
panel.grid.minor = element_blank(), 
axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
scale_x_discrete(breaks=seq(1989, 2020, 8)) + 
ylim(0, 150) + 
geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab, size =1), parse=FALSE)

>>>>

```{r plotSmallMultiples}
hIndex.df <- arrange(hIndex, desc(h5Median)) %>% select(title, h5Median)
hIndex.df$top10 <- NA
hIndex.df$top10[1:10] <- "Yes"
hIndex.df$top10[11:nrow(hIndex.df)] <- "No"
hIndex.df <- data.frame(hIndex.df)

@@

sm.df$top10 <- ifelse(is.na(sm.df$top10), "No", sm.df$top10)

@@

xpos = rep(12.5, 78)
ypos = rep(130, 78)
title2 <- unique(sm.df$title2)
lab <- paste("N=", Overall.N$Overall.N, sep="")

@@

ggplot(sm.df, aes(year, N, group=1)) + geom_line(aes(colour = top10)) + 
facet_wrap( ~ title2, ncol=7) +
theme_bw() +
theme(panel.grid.major = element_blank(), legend.position = "bottom", 
panel.grid.minor = element_blank(), 
axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
scale_x_discrete(breaks=seq(1989, 2020, 8)) + 
ylim(0, 150) + 
geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab), size =3) +
    scale_color_manual(values=cp[c(4,2)], 
                       name = "Top-10 Journal") + 
    ylab("") + 
    xlab("")
